Shooting Occurences in Toronto Have Increased Greatly All Throughout

### 2022-01-31 starter_folder-main/outputs/paper/paper.Rmd
save data
Completed visualizations

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Thomas D'Onofrio
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("palmerpenguins")
library(tidyverse)
library(palmerpenguins)
```

@@

>>>>

---
title: "Shooting Occurences in Toronto Have Increased Greatly All Throughout"
subtitle: "My subtitle if needed"
author: 
  - Thomas D'Onofrio
thanks: "Code and data are available at: https://github.com/TDonofrio62/Paper-1."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(knitr)
```

@@

(Table \@ref(fig:dataextract))
```{r datextract}

shooting_occurences <- read_csv(here::here("inputs/data/shooting_occurences.csv"))

shooting_occurences %>%
  slice(1,2,18,19,36,37,54,55,72,73,90,91) %>%
  select(occurred_year, geo_division, num_shootings) %>%
  kable(
    caption= "12 Observations from dataset of shooting occurences in Toronto",
    col.names = c("Year", "Geographic Division", "Number of Shootings"),
    booktabs = TRUE,
    linesep = "",
    align = c('c', 'c', 'c')
  )

```

```{r yearlyshootings}
shooting_occurences %>%
  select(occurred_year,num_shootings)%>%
  group_by(occurred_year)%>%
  summarize(number_of_shootings = sum(num_shootings)) %>%
  kable(
    caption= "Number of Shootings in Toronto each year from 2014-2019",
    col.names = c("Year", "Number of Shootings"),
    booktabs = TRUE,
    linesep = "",
    align = c('c', 'c')
  )

```

```{r, fig.cap= "Relationship between number of shootings in each police division and year"}
shooting_occurences %>%
  ggplot(aes(x = occurred_year, y = num_shootings, color = geo_division)) +
  geom_point()+
  theme_bw() +
  labs(x = "Year",
       y = "Number of Shootings",
       color = "Geographic Division"
       )
```

```{r}
shooting_occurences %>%
  ggplot(aes(x = geo_division, y = num_shootings, color = as.character(occurred_year))) +
  geom_point()+
  theme_bw() +
  labs(x = "Geographic Division",
       y = "Number of Shootings",
       color = "Year"
       )+
   scale_color_brewer(palette = "Set1", direction=-1)
```

```{r}
shooting_occurences %>%
  ggplot(aes(x = occurred_year, y = num_shootings, fill = geo_division)) + 
  geom_bar(stat='identity') +
  theme_bw() +
  labs(x = "Year",
       y = "Number of Shootings",
       fill = "Geographic Division"
       )
```

```{r}
shooting_occurences %>%
  ggplot(aes(x = geo_division, y = num_shootings, fill = as.character(occurred_year))) + 
  geom_bar(stat='identity') +
  theme_bw() +
  labs(x = "Geographic Division",
       y = "Number of Shootings",
       fill = "Year"
       )+
  scale_fill_viridis_d()
```
